An Experimental Analysis of the Influence of the Precision of Parameters in an Artificial Neural Network

### 2025-11-09 paper/main.tex
weiter

To reduce memory usage and computational load, precision-aware techniques such
as quantization and mixed-precision training are increasingly employed. Instead
of using 32-bit or 64-bit floating-point formats, parameters can be stored in
16-bit or even 8-bit fixed-point representations.
Figure~\ref{fig:floatingPointFormat} depicts the general floating point format
and terminology of significand, base, and exponent.
Tables~\ref{tab:binary-bits} and~\ref{tab:binary-precision} provide an overview
of the different floating point types and their respective characteristics.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/float.png}
	\caption{Illustration of standard floating-point format.}\label{fig:floatingPointFormat}
\end{figure}

>>>>

To reduce memory usage and computational load, precision-aware techniques such
as quantization and mixed-precision training are increasingly employed. Instead
of using 32-bit or 64-bit floating-point formats, parameters can be stored in
16-bit or even 8-bit fixed-point representations.
Equation~\ref{eq:floatingPointFormat} depicts the general floating point format
and terminology of significand, base, and exponent.
Tables~\ref{tab:binary-bits} and~\ref{tab:binary-precision} provide an overview
of the different floating point types and their respective characteristics.

\begin{align}\label{eq:floatingPointFormat}
	\frac{2469}{200}=12.345=\underbrace{12345}_{\text{significand}}\times\underbrace{10^{\overbrace{-3}^{\text{exponent}}}}_{\text{base}}
\end{align}
